---
name: Øystein Sørensen
position: "Associate Professor"
address: "Department of Psychology, University of Oslo"
www: osorensen.rbind.io
email: oystein.sorensen@psykologi.uio.no
twitter: SorensenOystein
github: osorensen
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
source("../scripts/install.R")
```

```{r get data, include=FALSE}
## Education
edu <- read_delim(here("data", "education.csv"), delim = ";")

## Jobs
jobs <- read_delim(here::here("data", "jobs.csv"), delim = ";")

## Editorial boards
editor <- read_delim(here::here("data", "editor.csv"), delim = ";")

## Grants
grants <- read_delim(here::here("data", "grants.csv"), delim = ";")

## Papers
get_papers <- function(bibfile){
  bib2df::bib2df(here::here("data", bibfile)) %>% 
    mutate(TITLE = str_remove_all(TITLE, "\\{|\\}")) %>% 
    mutate(MONTH = if_else(is.na(MONTH), "jan", MONTH),
      date = ymd(paste(YEAR, MONTH, "01", sep = "-"))) %>% 
    arrange(desc(date)) %>% 
    # put authors in one string
    mutate(
      author = map(AUTHOR, ~ glue_collapse(.x, sep = "; ")),
      author = str_replace(author, "^Vidal", "{Vidal")
      ) %>% 
    mutate(
      journal = if_else(is.na(JOURNAL), BOOKTITLE, JOURNAL),
      doi = textutils::TeXencode(DOI),
      where = ifelse(
        !is.na(doi),
        glue("<journal>. \\url{http://doi.org/<doi>}", .open = "<", .close = ">"),
        journal),
      first_author = str_detect(BIBTEXKEY, "sorensen") | 
        str_detect(BIBTEXKEY, "vitelli2017")
      ) %>% 
    arrange(desc(YEAR))
}

pubs <- get_papers("publications.bib")
preprints <- get_papers("preprints.bib")

## Software
software <- read_delim(here::here("data", "software.csv"), delim = ";") %>% 
  arrange(desc(when))

## Teaching
teaching <- read_delim(here::here("data", "teaching.csv"), delim = ";") %>% 
  arrange(desc(when))

## Courses and workshop
courses <- read_delim(here::here("data", "courses.csv"), delim = ";") %>% 
  arrange(desc(when))


## Presentations
presentations <- read_delim(here::here("data", "presentations.csv"), delim = ";") %>% 
  arrange(desc(when))

## Other presentations
communication <- read_delim(here::here("data", "communication.csv"), delim = ";") %>% 
  arrange(desc(when))

## Service
service <- read_delim(here::here("data", "service.csv"), delim = ";")
```

# Education
```{r}
detailed_entries(edu,
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = loc,
                 with = uni,
                 why = details)

```

# Experience

```{r research}
jobs %>%
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = company,
    where = where,
    why = details)
```

# Editorial Boards

```{r}
editor %>%
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = journal
  )
```

# Grants

```{r}
grants %>% 
  detailed_entries(
    what = project,
    with = role,
    when = glue("{start_date}--{end_date}"),
    why = details
  )
```


# Publications

*See [my Google Scholar profile](https://scholar.google.com/citations?user=neOqbw0AAAAJ&hl=no) for further information.*
\hfill\break

## First Author Publications



```{r}
pubs %>% 
  filter(first_author) %>% 
  detailed_entries(
    what = author,
    when = YEAR,
    with = TITLE,
    where = where,
    .protect = FALSE
  )
```

## Non First Author Publications

```{r}
pubs %>% 
  filter(!first_author) %>% 
  detailed_entries(
    what = author,
    when = YEAR,
    with = TITLE,
    where = where,
    .protect = FALSE
  )
```


## Preprints

```{r}
preprints %>%
  detailed_entries(
    what = author,
    when = YEAR,
    with = TITLE,
    where = where,
    .protect = FALSE
  )
```



# Software

*See [my GitHub](https://github.com/osorensen/) for a complete overview of my software both released and in development.*
\hfill\break


```{r}
software %>% 
  detailed_entries(what = what, when = when, with = with, where = where, why = why)
```




# Teaching

```{r}
teaching %>%
  detailed_entries(what = what, when = when, with = with, why = details, where = where)
```


# Courses and Workshops Organized

```{r}
courses %>%
  detailed_entries(what = what, when = when, with = with, why = details, where = where)
```


# Presentations at Peer-Reviewed International Conferences

```{r}
presentations %>%
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where,
                   why = why,
                   .protect = TRUE)
```


# Research Communication and Other Presentations

```{r}
communication %>%
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where,
                   why = why,
                   .protect = TRUE)
```

# Service

```{r}
service %>%
  detailed_entries(what = type, why = details)
```
